Volatility and the Buyback Anomaly: Interactive Tool

### 2017-02-17 manuscript.Rnw
rename

if (generate_all_data == 1){
  source("create_project_data.R")
}
if (generate_rnw_data == 1){
  source("process_project_data.R")
} else {
  load("processed_project_data.Rdata")
}

>>>>

if (generate_all_data == 1){
  source("create_project_data.R")
}
if (generate_rnw_data == 1){
  source("process_data_for_paper.R")
} else {
  load("data_for_paper.Rdata")
}
